Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
Spotted some more

\begin{abstract}
	In contrast to current demand for probabilistically interesting domains in the International Probabilistic Planning Competitions, this papier argues for using real-world appropriate domains. By relaxing the definition of a dead-end, we argue that for many
real life domains a simpler planning algorithm can be sufficient and even better than sophisticated probabilistic planners.

In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabistic problem against a state of the art probabilistic planner GOURMAND, the successor of the Labelled Real-Time Dynamic Probabilistic planner Glutton, runner up of the IPPC-11. By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equavalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et. all we will evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
\end{abstract}

@@

%\begin{itemize}
%	\item Describe probabilistic planning problem
%	\item Introduce planning for uncertainty
%	\item Describe how deterministic classical planners can be used in probabilistic domains and motivate why this is interesting
%	\item Introduce the qualities of replanning and the second planning algorithm
%	\item Describe the need for a new domain for real world applications
%	\item Describe the goal and tools used to reach this goal
%\end{itemize}

>>>>

\begin{abstract}
	This paper argues that for many real life domains dead-ends are the end of
	the world, and by for example human interaction the goal can still be
	reached. By relaxing the definition of a dead-end, we argue that for many
	real life domains a simpler planning algorithm, like FF-Replan, can be
	sufficient, and that it's not needed to have newer and sophisticated
	probabilistic planners.
\end{abstract}

@@

\begin{itemize}
	\item Describe probabilistic planning problem
	\item Introduce planning for uncertainty
	\item Describe how deterministic classical planners can be used in probabilistic domains and motivate why this is interesting
	\item Introduce the qualities of replanning and the second planning algorithm
	\item Describe the need for a new domain for real world applications
	\item Describe the goal and tools used to reach this goal
\end{itemize}
